Downward shortwave solar irradiance enhancement by clouds.

### 2024-04-15 article/article.tex
Commit 2024-04-16 02:14

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  preprint, 3p, authoryear]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Downward shortwave solar irradiance enhancement by clouds.},
  pdfkeywords={keyword1, keyword2},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Downward shortwave solar irradiance enhancement by clouds.}
\author{true \and true \and true}
\date{2024-04-14}

\begin{document}
\maketitle
\begin{abstract}
Here wii be the abstract.

It consists of two paragraphs.
\end{abstract}

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\hypertarget{abstract}{%
\section*{Abstract}\label{abstract}}
\addcontentsline{toc}{section}{Abstract}

@@

The shortwave solar irradiance, reaching Earth's surface, is the main energy source
of the atmosphere and biosphere and drives and governs the climate (Gray et al. 2010). It
has direct practical application, in different industries, like energy production and
agriculture method. The variability of its intensity, can cause difficulties in
predicting the yield, and designing the specifications of the appropriate equipment.
A lot of research has been focused on predicting the renewable energy production in a
fine timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).

@@

Some of the proposed underling mechanisms of those events, have been summarized by
Gueymard (2017), and include scattering on the edge of cumulus clouds or through thin
cirrus. Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015), through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness, constitution and type; and the relative position of the sun, the clouds,
and the observer (Gueymard 2017; Veerman, Van Stratum, and Van Heerwaarden 2022). As such, there are multiple
contributing mechanism that are responsible for the observed irradiance enhancements.

Cloud enhancements have been reported, to be able to exceed in intensity even the
value of the solar constant, resulting of clear indexes above unit. A summary of
extreme enchantment cases have been compiled by Martins, Mantelli, and Rüther (2022). There are also some
practical implication of the cloud enchantments. The intensity and duration of
enhancements can effect the efficiency and stability of photovoltaic power production
(Lappalainen and Kleissl 2020; Järvelä and Valkealahti 2020), and extreme enhancements cases, have the
potential to compromise the integrity of photovoltaic plants infrastructure
(Do Nascimento et al. 2019). It has also been demonstrated, that these events can interfere
in the comparison of ground data and satellite observations (Damiani et al. 2018)

Methods of identification cloud enchantment events in the literature, usually include
the use of a simulated clear sky radiation as baseline, that is combined with an
appropriate threshold or some other statistical characteristics, and in some cases,
with visual methods with a sky cam (Vamvakas, Salamalikis, and Kazantzidis 2020; Mol, Knap, and Van Heerwaarden 2023 and references therein).

@@

In the relative bibliography different definition have been used for these events,
some of the are summarized by Gueymard (2017). Here, we defined as cloud enhancement
events (CE) the cases when the measured global horizontal irradiance (GHI) at ground
level, exceeds the expected value under clear-sky conditions. Similar, we define as
extreme cloud enhancement events (ECE), the cases when GHI, exceeds the Total Solar
Irradiance on horizontal plane at ground level. Although the duration of these
bursts varies, from instantaneous to several minutes, here we are constrained by the
recorded data, to one-minute steps.

@@

To further improve the quality of the irradiance data, a manual screening was
performed to remove inconsistent and erroneous recordings that can occur
stochastically or systematically during the continuous operation of the instruments.
The manual screening was aided by a radiation data quality assurance procedure,
adjusted for the site, which was based on the methods of Long and Shi~(Long and Shi 2006, 2008). Thus, problematic recordings have been excluded from further
processing. Although it is impossible to detect all false data, the large number of
available data, and the aggregation scheme we used, ensures the quality of the
radiation measurements used in this study.
To preserve an unbiased representation of the data we applied a constraint, similar
the one used by Castillejo-Cuberos and Escobar (2020). Where, for each valid hour of day, there must
exist at least 45 minutes of valid measurements, including nighttime near sunrise and
sunset. Days with less than 5 valid hours are rejected completely.
Furthermore, due to the significant measurement uncertainty when the Sun is near the
horizon, and due to some systematic obstructions by nearby buildings, we have
excluded all measurements with solar zenith angle (SZA) greater than
\(78^\circ\).

@@

To be able to detect the CE cases, we had to establish a baseline, above which we can
characterize each data point as an enhancement event, by estimating the occurring
over irradiance (OIR). The OIR, here is defined as the irradiance difference of the
measured one-minute \(\text{GHI}_i\) from the CE identification criterion in
Equation\nobreakspace\ref{eq:CE4}
(\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)).
To have an estimation, and a first insight on the phenomenon, we experimented with two
simple approaches for the reference. The Haurwitz's model (Haurwitz 1945), which is
as simple clear sky model, and we had already adjusted and had good fit with our data
(Natsis, Bais, and Meleti 2023), and the TSI at the top of the atmosphere. We have tested both cases
by using an appropriate relative threshold and/or an additional constant offset. The
initial results, showed that we can detect a big portion of the CE events. These
results were helpful, and helped to establish some criteria to further improve the CE
identification. It was evident, by inspecting the daily plot of irradiance, that
changes on the atmospheric conditions introduced numerous false positive and false
negative results. To produce a more accurate reference, we had to take into account
more factors that effect the clear sky radiation. So we used a radiation transfer
model.

@@

We approximated the expected clear sky GHI by using a radiation transfer model. The
simulations was performed by the well established model Libradtran (Emde et al. 2016), a
similar approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020) for creating a clear sky reference.
Because of the lack of observational data for the whole period, we used some long
term climatological data for the main factors responsible for the attenuation of the
broadband downward solar radiation in the atmosphere. Which are mainly, the aerosols
and the water vapors. Fortunately, our site participates in the Aerosol Robotic
Network (AERONET) (Giles et al. 2019; Buis et al. 1998), as we operate a Cimel photometer since
2003, collocated with the CM-21 pyranometer. The mean monthly aerosol optical depth
(AOD) on different wavelengths is provided by AERONET, along with the equivalent
water column height in the atmosphere.

For completeness, we will describe here the main points of the radiation simulation
procedure. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
\(2500\,\text{nm}\), with the Libradtran radiation transfer solver ``disort'' on a
``pseudospherical'' geometry and the ``LOWTRAN'' gas parameterization. For each
combination of conditions we use a SZA step of \(0.2^\circ\).
For the atmospheric characteristics, we iterated for combinations of AOD at
\(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets of \(\pm1\) and
\(\pm2\sigma\), and water column (\(wc\)), also with offsets of \(\pm1\) and \(\pm2\sigma\).
We applied them on two atmospheric profiles, from the Air Force Geophysics
Laboratory (AFGL). The ``AFGL atmospheric constituent profile, midlatitude summer''
(afglms) and the ``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw)
(Anderson et al. 1986).

To create a look-up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability, in our one-minute GHI measurements,
we adapted each modeled value by scaling the\\
model's input spectrum integral, to the corresponding total solar irradiance (TSI)
provided by NOAA (Coddington et al. 2005).\\
Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
(Astropy Collaboration et al. 2022) software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements. For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw). Finally, we calculated
the clear sky irradiance value at the horizontal plane. Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site. With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

@@

To select the exact values of these thresholds factors (Equation \ref{eq:CE4}), we
implemented an empirical method, by manual inspection of the CE identification, on
specially selected days from the whole dataset. We used seven sets of selected days,
with characteristics relevant to the efficiency of the identification threshold.
These sets were random groups of about 20 to 30 days with the following
characteristics:
(a) the largest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) without clouds (by implementing a clear sky identification algorithm as discussed in Natsis, Bais, and Meleti (2023)),
(d) without clouds and without EC events,
(e) with at least \(60\,\%\) of the day length without clouds and some EC events,
(h) random days and
(i) some manual selected days that were included during the manual inspection.
Where it was needed, for some of the edge cases, we also used images from a sky-cam,
to further aid the decisions of the manual inspection.

@@

We computed the daily trend of the mean OIR of CE
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order autoregressive
model with lag of 1 day, using the `maximum likelihood' fitting method (Gardner, Harvey, and Phillips 1980; Jones 1980) by implementing the function `arima' from the library `stats' of the R
programming language (R Core Team 2023). The trends are reported together with the \(2\sigma\)
error. We observe an increase of
\(0.216\pm 0.083\,W/m^2/y\)
on the mean OIR.

@@

\ldots{} (\textbf{Zhang2018?}) \ldots.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Anderson1986}{}}%
Anderson, G. P., J. H. Chetwynd, S. A. Clough, E. P. Shettle, and F. X. Kneizys. 1986. {``{AFGL} Atmospheric Constituent Profiles (0-120km).''} Air Force Geophysics Laboratory, Optical Physics Division.

\leavevmode\vadjust pre{\hypertarget{ref-AstropyCollaboration2022}{}}%
Astropy Collaboration, Adrian M. Price-Whelan, Pey Lian Lim, Nicholas Earl, Nathaniel Starkman, Larry Bradley, David L. Shupe, et al. 2022. {``{The Astropy Project: Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package}.''} \emph{Astrophysical Journal} 935 (2): 167. \url{https://doi.org/10.3847/1538-4357/ac7c74}.

\leavevmode\vadjust pre{\hypertarget{ref-Buis1998}{}}%
Buis, J. P. P., A. Setzer, B. N. N. Holben, T. F. F. Eck, I. Slutsker, D. Tanre, E. Vermote, et al. 1998. {``AERONET---a Federated Instrument Network and Data Archive for Aerosol Characterization.''} \emph{Remote Sensing of Environment} 66 (1): 1--16.

\leavevmode\vadjust pre{\hypertarget{ref-CastillejoCuberos2020}{}}%
Castillejo-Cuberos, Armando, and Rodrigo Escobar. 2020. {``Detection and Characterization of Cloud Enhancement Events for Solar Irradiance Using a Model-Independent, Statistically-Driven Approach.''} \emph{Solar Energy} 209 (October): 547--67. \url{https://doi.org/10.1016/j.solener.2020.09.046}.

\leavevmode\vadjust pre{\hypertarget{ref-Coddington2005}{}}%
Coddington, Odele, Judith L. Lean, Doug Lindholm, Peter Pilewskie, Martin Snow, and NOAA CDR Program. 2005. {``{NOAA} Climate Data Record ({CDR}) of Total Solar Irradiance ({TSI}), {NRLTSI} Version 2. {D}aily.''} \url{https://doi.org/10.7289/V55B00C1}.

\leavevmode\vadjust pre{\hypertarget{ref-Damiani2018}{}}%
Damiani, Alessandro, Hitoshi Irie, Takashi Horio, Tamio Takamura, Pradeep Khatri, Hideaki Takenaka, Takashi Nagao, Takashi Y. Nakajima, and Raul R. Cordero. 2018. {``Evaluation of Himawari-8 Surface Downwelling Solar Radiation by Ground-Based Measurements.''} \emph{Atmos. Meas. Tech.}

\leavevmode\vadjust pre{\hypertarget{ref-DoNascimento2019}{}}%
Do Nascimento, Lucas Rafael, Trajano De Souza Viana, Rafael Antunes Campos, and Ricardo Rüther. 2019. {``Extreme Solar Overirradiance Events: Occurrence and Impacts on Utility-Scale Photovoltaic Power Plants in Brazil.''} \emph{Solar Energy} 186 (July): 370--81. \url{https://doi.org/10.1016/j.solener.2019.05.008}.

\leavevmode\vadjust pre{\hypertarget{ref-Emde2016}{}}%
Emde, Claudia, Robert Buras-Schnell, Arve Kylling, Bernhard Mayer, Josef Gasteiger, Ulrich Hamann, Jonas Kylling, et al. 2016. {``The {libRadtran} Software Package for Radiative Transfer Calculations (Version 2.0.1).''} \emph{Geoscientific Model Development} 9 (5): 1647--72. \url{https://doi.org/10.5194/gmd-9-1647-2016}.

\leavevmode\vadjust pre{\hypertarget{ref-Gardner1980}{}}%
Gardner, G., A. C. Harvey, and G. D. A. Phillips. 1980. {``Algorithm {AS} 154: An Algorithm for Exact Maximum Likelihood Estimation of Autoregressive-Moving Average Models by Means of Kalman Filtering.''} \emph{Applied Statistics} 29 (3): 311. \url{https://doi.org/10.2307/2346910}.

\leavevmode\vadjust pre{\hypertarget{ref-Giles2019}{}}%
Giles, David M., Alexander Sinyuk, Mikhail G. Sorokin, Joel S. Schafer, Alexander Smirnov, Ilya Slutsker, Thomas F. Eck, et al. 2019. {``Advancements in the Aerosol Robotic Network ({AERONET}) Version 3 Database -- Automated Near-Real-Time Quality Control Algorithm with Improved Cloud Screening for Sun Photometer Aerosol Optical Depth ({AOD}) Measurements.''} \emph{Atmospheric Measurement Techniques} 12 (1): 169--209. \url{https://doi.org/10.5194/amt-12-169-2019}.

\leavevmode\vadjust pre{\hypertarget{ref-Graabak2016}{}}%
Graabak, Ingeborg, and Magnus Korpås. 2016. {``Variability Characteristics of European Wind and Solar Power Resources---a Review.''} \emph{Energies} 9 (6): 449. \url{https://doi.org/10.3390/en9060449}.

\leavevmode\vadjust pre{\hypertarget{ref-Gray2010}{}}%
Gray, L. J., J. Beer, M. Geller, J. D. Haigh, M. Lockwood, K. Matthes, U. Cubasch, et al. 2010. {``{SOLAR} {INFLUENCES} {ON} {CLIMATE}.''} \emph{Reviews of Geophysics} 48 (4): RG4001. \url{https://doi.org/10.1029/2009RG000282}.

\leavevmode\vadjust pre{\hypertarget{ref-Gueymard2017}{}}%
Gueymard, Christian A. 2017. {``Cloud and Albedo Enhancement Impacts on Solar Irradiance Using High-Frequency Measurements from Thermopile and Photodiode Radiometers. Part 1: Impacts on Global Horizontal Irradiance.''} \emph{Solar Energy} 153: 755--65. \url{https://doi.org/gb283c}.

\leavevmode\vadjust pre{\hypertarget{ref-Haurwitz1945}{}}%
Haurwitz, Bernhard. 1945. {``Insolation in {Relation} to {Cloudiness} and {Cloud} {Density}.''} \emph{Journal of Meteorology} 2 (September): 154--66.

\leavevmode\vadjust pre{\hypertarget{ref-Inman2013}{}}%
Inman, Rich H., Hugo T. C. Pedro, and Carlos F. M. Coimbra. 2013. {``Solar Forecasting Methods for Renewable Energy Integration.''} \emph{Progress in Energy and Combustion Science} 39 (6): 535--76. \url{https://doi.org/10.1016/j.pecs.2013.06.002}.

\leavevmode\vadjust pre{\hypertarget{ref-Jaervelae2020}{}}%
Järvelä, Markku, and Seppo Valkealahti. 2020. {``Operation of a {PV} Power Plant During Overpower Events Caused by the Cloud Enhancement Phenomenon.''} \emph{Energies} 13 (9): 2185. \url{https://doi.org/10.3390/en13092185}.

\leavevmode\vadjust pre{\hypertarget{ref-Jones1980}{}}%
Jones, Richard H. 1980. {``Maximum Likelihood Fitting of {ARMA} Models to Time Series with Missing Observations.''} \emph{Technometrics} 22 (3): 389--95. \url{https://doi.org/10.1080/00401706.1980.10486171}.

\leavevmode\vadjust pre{\hypertarget{ref-Kurucz1994}{}}%
Kurucz, Robert L. 1994. {``Synthetic Infrared Spectra.''} In \emph{Infrared Solar Physics}, edited by D. M. Rabin, J. T. Jefferies, and C. Lindsey, 523--31. Dordrecht: Springer Netherlands.

\leavevmode\vadjust pre{\hypertarget{ref-Lappalainen2020}{}}%
Lappalainen, Kari, and Jan Kleissl. 2020. {``Analysis of the Cloud Enhancement Phenomenon and Its Effects on Photovoltaic Generators Based on Cloud Speed Sensor Measurements.''} \emph{Journal of Renewable and Sustainable Energy} 12 (4): 043502. \url{https://doi.org/10.1063/5.0007550}.

\leavevmode\vadjust pre{\hypertarget{ref-Long2006}{}}%
Long, Charles N., and Y. Shi. 2006. {``The QCRad Value Added Product: Surface Radiation Measurement Quality Control Testing, Including Climatology Configurable Limits.''} DOE/SC-ARM/TR-074. Office of Science, Office of Biological; Environmental Research, U.S. Department of Energy.

\leavevmode\vadjust pre{\hypertarget{ref-Long2008a}{}}%
---------. 2008. {``An Automated Quality Assessment and Control Algorithm for Surface Radiation Measurements.''} \emph{The Open Atmospheric Science Journal}, 23--37.

\leavevmode\vadjust pre{\hypertarget{ref-Martins2022}{}}%
Martins, G. L., S. L. Mantelli, and R. Rüther. 2022. {``Evaluating the Performance of Radiometers for Solar Overirradiance Events.''} \emph{Solar Energy} 231 (January): 47--56. \url{https://doi.org/10.1016/j.solener.2021.11.050}.

>>>>

\documentclass[preprint, 3p,
authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

\usepackage[hyphens]{url}

  \journal{An awesome journal} % Sets Journal name

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Downward shortwave solar irradiance enhancement by clouds.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}

\begin{frontmatter}

  \title{Downward shortwave solar irradiance enhancement by clouds.}
    \author[LAP]{Athanasios N. Natsis%
  \corref{cor1}%
  \fnref{1}}
   \ead{natsisphysicist@gmail.com} 
    \author[LAP]{Alkiviadis Bais%
  %
  }
   \ead{abais@auth.gr} 
    \author[LAP]{Charikleia Meleti%
  %
  \fnref{2}}
   \ead{meleti@auth.gr} 
      \affiliation[LAP]{
    organization={Laboratory of Atmospheric Physics,
A.U.Th.},addressline={1 main
street},city={Thessaloniki},postcode={123456},country={Greece},}
    \affiliation[Another University]{
    organization={Department},addressline={A street
29},city={Manchester,},postcode={2054 NX},state={State},country={The
Netherlands},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

  \begin{abstract}
  Here wii be the abstract.

  It consists of two paragraphs.
  \end{abstract}
    \begin{keyword}
    keyword1 \sep 
    keyword2
  \end{keyword}

 \end{frontmatter}

\hypertarget{abstract}{%
\section*{Abstract}\label{abstract}}
\addcontentsline{toc}{section}{Abstract}

@@

The shortwave solar irradiance, reaching Earth's surface, is the main
energy source of the atmosphere and biosphere and drives and governs the
climate \citep{Gray2010}. It has direct practical application, in
different industries, like energy production and agriculture method. The
variability of its intensity, can cause difficulties in predicting the
yield, and designing the specifications of the appropriate equipment. A
lot of research has been focused on predicting the renewable energy
production in a fine timescale and in near real-time (for a review see
\citet{Inman2013}; \citet{Graabak2016}).

@@

Some of the proposed underling mechanisms of those events, have been
summarized by \citet{Gueymard2017}, and include scattering on the edge
of cumulus clouds or through thin cirrus. Further investigation with
radiation transfer modeling methods and observations have pointed as the
prevailing mechanism, the forward Mie scattering
\citep{Pecenak2016, Thuillier2013, Yordanov2013, Yordanov2015}, through
the clouds. The overall phenomenon depends on different interactive
factors, that include cloud thickness, constitution and type; and the
relative position of the sun, the clouds, and the observer
\citep{Gueymard2017, Veerman2022}. As such, there are multiple
contributing mechanism that are responsible for the observed irradiance
enhancements.

Cloud enhancements have been reported, to be able to exceed in intensity
even the value of the solar constant, resulting of clear indexes above
unit. A summary of extreme enchantment cases have been compiled by
\citet{Martins2022}. There are also some practical implication of the
cloud enchantments. The intensity and duration of enhancements can
effect the efficiency and stability of photovoltaic power production
\citep{Lappalainen2020, Jaervelae2020}, and extreme enhancements cases,
have the potential to compromise the integrity of photovoltaic plants
infrastructure \citep{DoNascimento2019}. It has also been demonstrated,
that these events can interfere in the comparison of ground data and
satellite observations \citep{Damiani2018}

Methods of identification cloud enchantment events in the literature,
usually include the use of a simulated clear sky radiation as baseline,
that is combined with an appropriate threshold or some other statistical
characteristics, and in some cases, with visual methods with a sky cam
\citep[ and references therein]{Vamvakas2020, Mol2023}.

@@

In the relative bibliography different definition have been used for
these events, some of the are summarized by \citet{Gueymard2017}. Here,
we defined as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected
value under clear-sky conditions. Similar, we define as extreme cloud
enhancement events (ECE), the cases when GHI, exceeds the Total Solar
Irradiance on horizontal plane at ground level. Although the duration of
these bursts varies, from instantaneous to several minutes, here we are
constrained by the recorded data, to one-minute steps.

@@

To further improve the quality of the irradiance data, a manual
screening was performed to remove inconsistent and erroneous recordings
that can occur stochastically or systematically during the continuous
operation of the instruments. The manual screening was aided by a
radiation data quality assurance procedure, adjusted for the site, which
was based on the methods of Long and Shi~\citep{Long2006, Long2008a}.
Thus, problematic recordings have been excluded from further processing.
Although it is impossible to detect all false data, the large number of
available data, and the aggregation scheme we used, ensures the quality
of the radiation measurements used in this study. To preserve an
unbiased representation of the data we applied a constraint, similar the
one used by \citet{CastillejoCuberos2020}. Where, for each valid hour of
day, there must exist at least 45 minutes of valid measurements,
including nighttime near sunrise and sunset. Days with less than 5 valid
hours are rejected completely. Furthermore, due to the significant
measurement uncertainty when the Sun is near the horizon, and due to
some systematic obstructions by nearby buildings, we have excluded all
measurements with solar zenith angle (SZA) greater than \(78^\circ\).

@@

To be able to detect the CE cases, we had to establish a baseline, above
which we can characterize each data point as an enhancement event, by
estimating the occurring over irradiance (OIR). The OIR, here is defined
as the irradiance difference of the measured one-minute \(\text{GHI}_i\)
from the CE identification criterion in
Equation\nobreakspace\ref{eq:CE4}
(\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)). To have an
estimation, and a first insight on the phenomenon, we experimented with
two simple approaches for the reference. The Haurwitz's model
\citep{Haurwitz1945}, which is as simple clear sky model, and we had
already adjusted and had good fit with our data \citep{Natsis2023}, and
the TSI at the top of the atmosphere. We have tested both cases by using
an appropriate relative threshold and/or an additional constant offset.
The initial results, showed that we can detect a big portion of the CE
events. These results were helpful, and helped to establish some
criteria to further improve the CE identification. It was evident, by
inspecting the daily plot of irradiance, that changes on the atmospheric
conditions introduced numerous false positive and false negative
results. To produce a more accurate reference, we had to take into
account more factors that effect the clear sky radiation. So we used a
radiation transfer model.

@@

We approximated the expected clear sky GHI by using a radiation transfer
model. The simulations was performed by the well established model
Libradtran \citep{Emde2016}, a similar approach, was also used by
\citet{Vamvakas2020} for creating a clear sky reference. Because of the
lack of observational data for the whole period, we used some long term
climatological data for the main factors responsible for the attenuation
of the broadband downward solar radiation in the atmosphere. Which are
mainly, the aerosols and the water vapors. Fortunately, our site
participates in the Aerosol Robotic Network (AERONET)
\citep{Giles2019, Buis1998}, as we operate a Cimel photometer since
2003, collocated with the CM-21 pyranometer. The mean monthly aerosol
optical depth (AOD) on different wavelengths is provided by AERONET,
along with the equivalent water column height in the atmosphere.

For completeness, we will describe here the main points of the radiation
simulation procedure. We used as input the spectrum of
\citet{Kurucz1994} in the range \(280\) to \(2500\,\text{nm}\), with the
Libradtran radiation transfer solver ``disort'' on a ``pseudospherical''
geometry and the ``LOWTRAN'' gas parameterization. For each combination
of conditions we use a SZA step of \(0.2^\circ\). For the atmospheric
characteristics, we iterated for combinations of AOD at
\(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets of
\(\pm1\) and \(\pm2\sigma\), and water column (\(wc\)), also with
offsets of \(\pm1\) and \(\pm2\sigma\). We applied them on two
atmospheric profiles, from the Air Force Geophysics Laboratory (AFGL).
The ``AFGL atmospheric constituent profile, midlatitude summer''
(afglms) and the ``AFGL atmospheric constituent profile, midlatitude
winter'' (afglmw) \citep{Anderson1986}.

To create a look-up table that aligns with our dataset, we applied some
adjustments. To account for the Sun's variability, in our one-minute GHI
measurements, we adapted each modeled value by scaling the\\
model's input spectrum integral, to the corresponding total solar
irradiance (TSI) provided by NOAA \citep{Coddington2005}.\\
Also, we applied the effect of the Earth -- Sun distance on the
irradiance, by using the distance calculated by the Astropy
\citep{AstropyCollaboration2022} software library. As needed, we
interpolate the resulting irradiances to the exact SZA of our
measurements. For each period of the year, we used the appropriate
atmospheric profile (afglms or afglmw). Finally, we calculated the clear
sky irradiance value at the horizontal plane. Thus, we were able to
emulate different atmospheric condition and levels of atmospheric
clearness for the climatological conditions of the site. With this
method, the modeled clear sky irradiances can be directly compared to
each measured one-minute value of GHI, for different conditions of
atmospheric clearness.

@@

To select the exact values of these thresholds factors (Equation
\ref{eq:CE4}), we implemented an empirical method, by manual inspection
of the CE identification, on specially selected days from the whole
dataset. We used seven sets of selected days, with characteristics
relevant to the efficiency of the identification threshold. These sets
were random groups of about 20 to 30 days with the following
characteristics: (a) the largest over irradiance CE events, (b) the
largest daily total over irradiance, (c) without clouds (by implementing
a clear sky identification algorithm as discussed in
\citet{Natsis2023}), (d) without clouds and without EC events, (e) with
at least \(60\,\%\) of the day length without clouds and some EC events,
(h) random days and (i) some manual selected days that were included
during the manual inspection. Where it was needed, for some of the edge
cases, we also used images from a sky-cam, to further aid the decisions
of the manual inspection.

@@

We computed the daily trend of the mean OIR of CE
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order
autoregressive model with lag of 1 day, using the `maximum likelihood'
fitting method \citep{Gardner1980, Jones1980} by implementing the
function `arima' from the library `stats' of the R programming language
\citep{RCT2023}. The trends are reported together with the \(2\sigma\)
error. We observe an increase of \(0.216\pm 0.083\,W/m^2/y\) on the mean
OIR.

@@

\ldots{} \citet{Zhang2018} \ldots.

@@

\bibliography{bibliography.bib}
